Optimal Parameter Selection in Markov State Models for Biomolecular Conformational Dynamics

### 2013-11-25 paper/paper2.tex
final figs

\begin{figure}
\centering
\includegraphics[width=3.1in]{figs/overfitting.png}
\caption{An example of overfitting. Left: in the presence of noise, a more complex model is able to fit the observed training data better, with lower residues and a higher empirical likelihood, but fails to distinguish the signal from the noise. Right: more complex model classes exhibit lower training errors, but generalize poorly to unobserved data.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=3in]{figs/mull_ww.png}
\caption{Systems studied in this work. (A) Langevin dynamics on the two dimensional M\"{u}ller potential. (b) 200 $\mu s$ of dynamics of the Fip35 WW domain\cite{Liu2008Experimental}, courtesy of D.E. Shaw research \cite{Shaw2010Atomic}.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=2in]{figs/mull_cross_vert.png}
\caption{In models built using between 50 and 1,000 states with the $k$-centers algorithm, the log likelihood function increased quickly and plateaued at approximately 300 states. There are many methods that can be used to test the transferability of an MSM. We've plotted the AIC, BIC, and cross-validation scores for the M\"uller potential simulations. These results indicate that, at least for this dataset, the BIC and AIC may penalize the number of states too heavily.}
\label{fig:mullerlike}
\end{figure}

>>>>

%\begin{figure}
%\centering
%\includegraphics[width=3.1in]{figs/overfitting.png}
%\caption{An example of overfitting. Left: in the presence of noise, a more complex model is able to fit the observed training data better, with lower residues and a higher empirical likelihood, %but fails to distinguish the signal from the noise. Right: more complex model classes exhibit lower training errors, but generalize poorly to unobserved data.}
%\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=3in]{figs_final/mull_ww.png}
\caption{Systems studied in this work. (A) Langevin dynamics on the two dimensional M\"{u}ller potential. (b) 200 $\mu s$ of dynamics of the Fip35 WW domain\cite{Liu2008Experimental}, courtesy of D.E. Shaw research \cite{Shaw2010Atomic}.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=2in]{figs_final/mull_cross_vert.png}
\caption{In models built using between 50 and 1,000 states with the $k$-centers algorithm, the log likelihood function increased quickly and plateaued at approximately 300 states. There are many methods that can be used to test the transferability of an MSM. We've plotted the AIC, BIC, and cross-validation scores for the M\"uller potential simulations. These results indicate that, at least for this dataset, the BIC and AIC may penalize the number of states too heavily.}
\label{fig:mullerlike}
\end{figure}
